How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-27 docs/PhysicsPaper/StokesErosion.tex
NM

Figure~\ref{fig5}(c) shows the corresponding statistics of anisotropy, $\anis$. Here, the anisotropy is not as well separated by $M$. That is, given the error-bars, there is significant overlap in the signal of $\anis$ across different values of $M$. On notable feature is second rise in $\anis$ that occurs late in the simulation only for the larger values of $M$ = 60, 80, and 100. As before, the anisotropy can be decomposed into configuration and shape components as shown in Figs.~\ref{fig5}(d)--(e)

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.99 \textwidth]{./figs/fig5.pdf}
\caption{
a) Statistics from an ensemble of runs.
\label{fig5}
}
\end{figure*}
%---------------------------------------------------------%

>>>>

Figure~\ref{fig5}(c) shows the corresponding statistics of anisotropy, $\anis$. Here, the anisotropy is not as well separated by $M$. That is, given the error-bars, there is significant overlap in the signal of $\anis$ across different values of $M$. On notable feature is second rise in $\anis$ that occurs late in the simulation only for the larger values of $M$ = 60, 80, and 100. As before, the anisotropy can be decomposed into configuration and shape components as shown in Figs.~\ref{fig5}(d)--(e). Here, we see the late surge in configurational anisotropy for these larger values of $M = $ 60, 80, 100. For these runs with a large number of bodies, the latest stages of erosion are dominated by channelization which substantially promotes the configurational anisotropy. The shape anisotropy, meanwhile, takes a more regular, parabolic form that is relatively insensitive to the number of bodies.

%---------------------------------------------------------%
\begin{figure*}%[htbp]
\centering
\includegraphics[width = 0.99 \textwidth]{./figs/fig5.pdf}
\caption{ Permeability and anisotropy statistics from an ensemble of simulations.
a) 
\label{fig5}
}
\end{figure*}
%---------------------------------------------------------%
